What covert verbal actions tell us about the interplay between language, action, and perception

### 2021-04-16 manuscript.tex
minor updates to figures

The ability to examine our private thoughts is central to our subjective experience... Motor imagery can be defined as the mental process by which one rehearses an action without engaging in the physical movements involved in this particular action...

Because speech production results from sequences of motor commands which are assembled to reach a given communication goal, it belongs to the broader category of motor actions \citep{jeannerod_motor_2006}. Therefore, a parallel can be drawn between covert speech and other forms of covert verbal actions (e.g., covert signing, covert writing, covert typing) and, more generally, of motor imagery \citep{alderson-day_inner_2015, perrone-bertolotti_what_2014, loevenbruck_cognitive_2018}...

Briefly presenting the simulation and emulation theories of motor imagery. What about covert speech? Recent models and relation to the simulation/emulation theories of motor imagery...

In this perspective, we explore some of the theoretical and experimental consequences of considering covert verbal actions (e.g., covert speech, covert typing) as inhibited verbal actions... We explore two main themes. First, how is produced... Second... by joining together results from motor imagery, motor inhibition, and covert speech research, we highlight some...

@@

How does motor learning/experience influence the multisensory content/experience of motor imagery and covert verbal actions? In other words, how to the motor and perceptual system interact during covert verbal actions? In the first subsection, we discuss two mechanisms that may be responsible for providing the sensory content of covert verbal actions and their respective involvement and delimitation. In the second subsection, we discuss an exciting avenue for investigating the influence of motor learning on the sensory content of imagined actions, namely studying the imagery ot totally novel (i.e., never executed) actions...

@@

One obvious difference subsist between overt and covert verbal actions, namely that covert actions are not accompanied by overt movements... This puzzle, coined as \textit{the problem of inhibition} by \cite{jeannerod_neural_2001}, can be summarised as follows: given the putative role of the motor system in providing the multisensory perceptual content of motor imagery, how is it possible for motor imagery not to lead to motor execution? We outline some working hypotheses regarding these mechanisms and their plausible roles in certain inhibitory disorders...

@@

Inhibitory mechanisms underlying the ability to imagine actions \citep{guillot_imagining_2012, schwoebel_man_2002}... For the sake of clarity, we need to make a distinction between at least two different types of inhibition: the inhibition of physical response (e.g., planning to raise the arm and finally not doing it), and the idea of cognitive inhibition, defined as "the stopping or overriding of a mental process, in whole or in part, with or without intention" \citep{gorfein_concept_2007}. In the current project, we are concerned with the former, which can be defined broadly as the withholding, suppression, or overriding of an inappropriate, prepotent, or unwanted motor response \citep{aron_neural_2007, oshea_go_2018}.

To be even more precise, \cite{ridderinkhof_dont_2014} described the concept of response inhibition on three continuous dimensions (intentionality, premeditation, specificity). Inhibition can be employed with more or less intentionality (intentional vs. reactive inhibition), planned ahead or employed in the moment (early vs. late inhibition), and more or less specifically (global inhibition versus effector-specific or action-specific inhibition). More detailed categorisation of inhibitory mechanisms can occur in this three-dimensional space but for the current purpose it is sufficient to say that we are interested (purportedly) in an intentional (we know we want to produce motor imagery rather than overt execution) but automatic (we do not explicitly think about not producing movements), planned ahead (proactive), and possibly global form of response inhibition...

Neural correlates... the inhibitory triangle (cf. Figure \ref{fig:2}), composed of the preSMA, the rIFC, and the STN... A functional dissociation between the preSMA and the rIFC \citep{diesburg_pause-then-cancel_2021}... Moreover, they also reported a reduced short-interval intracortical inhibition (SICI) in patients with TS, a phenomenon that has been shown to be involved in response inhibition during motor imagery \citep{neige_unravelling_2020}...

@@

\begin{figure}[ht] % float was h! initially
\begin{center}
\includegraphics[width=0.75\textwidth]{figures/association_simulation.png} % This is a *.eps file
\end{center}
\caption{The balance (weighing) of the prediction-by-simulation (in blue) and prediction-by-association (in orange) mechanisms during covert verbal actions depends on both internal (individual) and external (situational) characteristics that jointly determine the computation cost of each option... FIGURE IN PROGRESS.}\label{fig:1}
\end{figure}

\begin{figure}[ht] % float was h! initially
\begin{center}
\includegraphics[width=0.75\textwidth]{figures/inhibitory_triangle.png} % This is a *.eps file
\end{center}
\caption{Neural implementation of the inhibitory mechanisms responsible for proactive inhibition. The cerebral complex formed by the preSMA, the rIFC and the STN is known as the inhibitory triangle may be responsible for braking motor commands... FIGURE IN PROGRESS.}\label{fig:2}
\end{figure}

>>>>

The ability to mentally examine our thoughts is central to our subjective experience. Mentally anticipating or rehearsing (verbal) actions allows us to become better at performing them (citation), to explore novel situations (citation), or to (citation)... Broadly construed, motor imagery can be defined as the mental process by which one rehearses an action without engaging in the physical movements involved in this particular action. Because speech production results from sequences of motor commands which are assembled to reach a given communication goal, it belongs to the broader category of motor actions \citep{jeannerod_motor_2006}. Therefore, a parallel can be drawn between covert speech (also known as \textit{inner speech} or \textit{speech imagery}) and other forms of covert verbal actions (e.g., covert signing, covert writing, covert typing) and, more generally, of motor imagery \citep{alderson-day_inner_2015, perrone-bertolotti_what_2014, loevenbruck_cognitive_2018}.

One of the most influential theoretical model of this broad phenomenon, the motor simulation theory \cite{jeannerod_origin_2006, jeannerod_representing_1994, jeannerod_neural_2001}, contains the three following postulates: i) there exists a continuum between the covert (the mental representation) and the overt execution of an action, ii) action representations can operate off-line, via a simulation mechanism, and iii) covert actions rely on the same set of mechanisms as the overt actions they simulate, except that execution is inhibited (O’Shea \& Moran, 2017). A second class of explanatory models of motor imagery are concerned with the phenomenon of emulation and with internal models (see Gentsch et al., 2016, for a review of the similarities and dissimilarities between simulation and emulation models). Internal model theories share the postulate that action control uses internal models, that is, systems that simulate the behaviour of the motor apparatus (Jordan \& Rumelhart, 1992; Kawato et al., 1987). The function of internal models is to estimate and anticipate the outcome of a motor command. Among the internal model theories, motor control models based on robotic principles (e.g., Kawato, 1999; Wolpert et al., 1995) assume two kinds of internal models (that are supposed to be coupled and regulated): a forward model (or simulator) that predicts the sensory consequences of motor commands from efference copies of the issued motor commands, and an inverse model (or controller) that calculates the feedforward motor commands from the desired sensory states \cite{gentsch_towards_2016, loevenbruck_cognitive_2018}. Notice that in the following, we do not distinguish further between simulation and emulation, and we use these terms interchangeably to designate the mechanism through which sensory consequences of motor commands (or copy thereof) are computed by forward internal models...

% Because speech production results from sequences of motor commands which are assembled to reach a given communication goal, it belongs to the broader category of motor actions \citep{jeannerod_motor_2006}. Therefore, a parallel can be drawn between covert speech (also known as \textit{inner speech} or \textit{speech imagery}) and other forms of covert verbal actions (e.g., covert signing, covert writing, covert typing) and, more generally, of motor imagery \citep{alderson-day_inner_2015, perrone-bertolotti_what_2014, loevenbruck_cognitive_2018}...

By building upon models of motor control (e.g., Houde \& Nagarajan, 2011; Wolpert et al., 1995), a recent model describes wilful (voluntary) expanded covert speech as "multi-modal acts with multi-sensory percepts stemming from coarse multi-sensory goals" (L\oe venbruck et al., 2018). In other words, this model considers the auditory and kinaesthetic sensations perceived during covert speech to be the predicted sensory consequences of inhibited speech motor acts, emulated by internal forward models that use the efference copies issued from an inverse model (this proposal shares some similarities with the emulation model of motor imagery, Grush, 2004). This model is supported by several empirical results providing both behavioural and neurophysiological evidence for the efference copies issued during inner speech production (e.g., Scott, 2013; Whitford et al., 2017)...

In this perspective, we explore some theoretical and experimental consequences of considering covert verbal actions (e.g., covert speech, covert typing) as inhibited verbal actions. We explore two main themes. First, we discuss the plausible origins of the sensory (e.g., auditory, tactile) content of covert verbal actions. Second, we discuss the under-explored role of inhibitory mechanisms during motor imagery and covert verbal actions. By bridging together recent results from motor imagery, motor inhibition, and inner speech research, we highlight some novel and possibly fruitful lines of research.

@@

How does motor learning/experience influence the multisensory content/experience of motor imagery and covert verbal actions? In other words, how to the motor and perceptual system interact during covert verbal actions? In the first subsection, we discuss two mechanisms that may be responsible for providing the sensory content of covert verbal actions and their respective involvement and delimitation. In the second subsection, we discuss an exciting avenue for investigating the influence of motor learning on the sensory content of imagined actions, namely studying the imagery of totally novel (i.e., never executed) actions...

@@

The proposal that overt and covert actions share common/similar neural circuits is faced with a serious problem. If the neural circuits used for the control of overt actions are reused for covert actions, how can covert actions not lead to execution? This puzzle, coined as \textit{the problem of inhibition} by \cite{jeannerod_neural_2001}, can be rephrased as follows: given the putative role of the motor system in providing the multisensory perceptual content of motor imagery, how is it possible for motor imagery not to lead to motor execution? In the following, we briefly summarise the evidence in favour of the view of covert verbal actions as inhibited verbal actions. Then, we discuss the relations between this view and the supposed progressive internalisation of speech in childhood. Finally, we outline some working hypotheses regarding the cognitive and neural implementation of these inhibitory mechanisms and their plausible roles in psychological disorders.

@@

First and foremost, we need to make a distinction between at least two different types of inhibition: the inhibition of physical response (e.g., planning to raise the arm and finally not doing it), and the idea of cognitive inhibition, defined as "the stopping or overriding of a mental process, in whole or in part, with or without intention" \citep{gorfein_concept_2007}. Here we are concerned with the former, which can be defined broadly as the withholding, suppression, or overriding of an inappropriate, prepotent, or unwanted motor response \citep{aron_neural_2007, oshea_go_2018}. To be even more precise, \cite{ridderinkhof_dont_2014} described the concept of response inhibition on three continuous dimensions: intentionality, premeditation, specificity. Inhibition can be employed with more or less intentionality (intentional vs. reactive inhibition), it can planned ahead or employed in the moment (early vs. late inhibition), and it can be more or less specifically (global inhibition versus effector-specific or action-specific inhibition).

More detailed categorisation of inhibitory mechanisms can occur at any location in this three-dimensional space but for the current purpose it is sufficient to say that we are interested (purportedly) in an intentional (we know we want to produce motor imagery rather than overt execution) but automatic (we do not explicitly think about not producing movements), planned ahead (proactive), and possibly global form of response inhibition... or maybe both global and effector-specifi, cf. the results of \cite{rieger_inhibition_2017}...

Inhibitory mechanisms underlying the ability to imagine actions \citep{guillot_imagining_2012, schwoebel_man_2002}. Neural correlates... the inhibitory triangle (cf. Figure \ref{fig:2}), composed of the preSMA, the rIFC, and the STN... A functional dissociation between the preSMA and the rIFC \citep{diesburg_pause-then-cancel_2021}... Moreover, they also reported a reduced short-interval intracortical inhibition (SICI) in patients with TS, a phenomenon that has been shown to be involved in response inhibition during motor imagery \citep{neige_unravelling_2020}...

@@

\begin{figure}[ht] % float was h! initially
\begin{center}
\includegraphics[width=0.75\textwidth]{figures/simulation_association.png} % This is a *.eps file
\end{center}
\caption{High-level depiction of the prediction-by-simulation (in blue) and prediction-by-association (in orange) mechanisms. The balance (weighting) between these two mechanisms during covert verbal actions depends on both task demands and "computational cost" (cf. text for more details), which are jointly determined by internal (individual) and external (situational) characteristics (e.g., expertise or (equivalently) task difficulty, noise, feedback perturbation).}\label{fig:1}
\end{figure}

\begin{figure}[ht] % float was h! initially
\begin{center}
\includegraphics[width=0.75\textwidth]{figures/inhibitory_triangle.png} % This is a *.eps file
\end{center}
\caption{Plausible neural implementation of the (cortical and subcortical) inhibitory mechanisms responsible for proactive inhibition during motor imagery. The preSMA, the right pIFC, and the STN together form an \textit{inhibitory network} known as the \textit{inhibitory triangle}, which may be responsible for braking motor commands during covert speech production... Created with BioRender.com... FIGURE IN PROGRESS.}\label{fig:2}
\end{figure}
